The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-07 paper.tex
update

The main purpose of this study is to use three-dimensional\
special relativistic hydrodynamics simulations\
involving CR jet injections from the central SMBH in the Galaxy to investigate\
whether the \textit{inclined} jet scenario is able to produce\
the \textit{symmetric} Galactic bubbles that are\
consistent with the observed features, including the shape, the\
surface brightness (for eROSITA bubbles), and the spectra (for \textit{Fermi} bubbles).\

@@

The correlation between the multi-wavelength simulation suggest that\
the \textit{Fermi} bubbles are produced by high-energy electrons\
via an inverse Compton scattering process, as the same electrons can\
also simultaneously produce synchrotron radiations in the\
presence of magnetic fields.

>>>>

The main purpose of this study is to use three-dimensional\
special relativistic hydrodynamics simulations\
involving CR jet injections from the central SMBH in the Galaxy to investigate\
whether the \textit{inclined} jet scenario is able to produce\
the \textit{symmetric} Galactic bubbles that are\
consistent with the observed features, including the shape, the\
surface brightness, and the spectra of \textit{Fermi} and microwave haze \citep{Dobler_2008,PlanckCollaborationIX2013}.

@@
